---
title: "Reproducible <br> Analytical Pipelines <br> in NHS Scotland"
subtitle: "Transforming Publishing Programme"
author: 'Anna Price <br> Information Services Division <br>'
date: "May 28, 2019 <br><br> Slides: https://github.com/annahprice/RAP-champions"
output:
  ioslides_presentation:
    css: my-theme.css
---

```{r setup, include = FALSE}
library(knitr)
library(magrittr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE)

# Create data frame for levels of automation table
automation_levels <- data.frame(c(1:3, c("4a", "4b"), 5:7),
                                c("Ad hoc R code",
                                  "R project",
                                  "R project under version control (VC)",
                                  "R project under VC and peer reviewed (wrangling)",
                                  "Replicable report in Rmarkdown (publication)",
                                  "Near RAP (VC, peer review, data quality assurance)",
                                  "Full RAP (as above plus unit testing and documentation)",
                                  "R package"))

```

## Introductions

- The Information Services Division (ISD) of the National Health Service (NHS) Scotland produces around 200 official and national statistics publications each year.
- Traditional publication format is a **static pdf document** with accompanying **excel tables**.
- Production uses **proprietary software** and is **time-consuming**, involving extensive manual formatting and checking.

## Introductions

Introduce the three of us, contact details and our roles on the team

Contact Transforming Publishing: nss.isdtransformingpublishing@nhs.net

[Transforming Publishing web pages](http://www.isdscotland.org/Products-and-Services/Transforming-Publishing-Programme/)

[Transforming Publishing on GitHub](https://github.com/NHS-NSS-transforming-publications)

[PHI on GitHub](https://github.com/Health-SocialCare-Scotland)

## What is a RAP project?

- No (or few) manual steps = data and output produced using code
- High quality and auditable = version control
- Sustainable = peer review

"Bells and whistles" include writing functions, documenting/testing these functions, package management and computing environment control.

## Levels of RAP/automation

```{r, echo = FALSE}
    kable(automation_levels,
          col.names = c("Level", "Description"),
          format = "markdown")
```

## Challenges

- Senior management buy in
- Culture change (peer review and working in the open)
- New software such as R and git
- Required development time
- Range of data sources and/or unstable production process
- IT (R and version control)

## IT Infrastructure

- R desktop and server
- RStudio Server Pro
- git
- GitHub/Gitea

## Questions

Experience with similar challenges in other organisations?
